A meta-analysis of mental rotation ability in the first years of life

### 2022-04-29 code/analysis.Rmd
Fix ICC and hypotheses for `brm_reg`

# Meta-regression with gender, age, and task
res_reg <- rma.mv(
  gi, vi,
  mods = ~ gender * age_c + task,
  random = ~ 1 | article / experiment,
  data = dat_reg,
  slab = experiment
)
print(res_reg)
# forest(res_full)

# Compute reduction in heterogeneity compared to the original meta-analysis
1 - (sd_article_reg + sd_experiment_reg) / (sd_article + sd_experiment)

# Compute probabilities of the different effects being greater than 0
hypothesis(res_brm_reg, "gender3M2 > 0")$hypothesis
hypothesis(res_brm_reg, "gender2M1 < 0")$hypothesis
hypothesis(res_brm_reg, "task2M1 > 0")$hypothesis
```

@@

# Run Bayesian multilevel model
res_brm_reg <- update(res_prior_reg, sample_prior = FALSE)
summary(res_brm_reg)
# plot(res_brm_reg)
```

>>>>

# Meta-regression with gender, age, and task
res_reg <- rma.mv(
  gi, vi,
  mods = ~ gender * age_c + task,
  random = ~ 1 | article / experiment,
  data = dat_reg,
  slab = experiment
)
print(res_reg)
# forest(res_full)
```

@@

# Run Bayesian multilevel model
res_brm_reg <- update(res_prior_reg, sample_prior = FALSE)
summary(res_brm_reg)
# plot(res_brm_reg)

# Compute probabilities of the different effects being greater than 0
hypothesis(res_brm_reg, "gender3M2 > 0")$hypothesis
hypothesis(res_brm_reg, "gender2M1 < 0")$hypothesis
hypothesis(res_brm_reg, "task2M1 > 0")$hypothesis

# Compute reduction in heterogeneity compared to the original meta-analysis
1 - (sd_article_reg + sd_experiment_reg) / (sd_article + sd_experiment)
```
